---
title: "Lab 00 - Hello IDS!"
author: "Adi Hirasaki"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Adi", "Niharika", "Collin", 
           "Xu Sun/Emily", "Xiu Feng/Judy", "Cecilia"),
  github_username = c("adi-smh", "niharirajanala-bot", "CollinMegson", 
                      "emily-username", "xiufengzhu992", "s2780666"), 
  colour = c("pink", "lavender", "cornflowerblue", 
             "lightblue", "black", "lightgoldenrod"),
  hobby = c("theatre", "reading", "tennis", 
            "ice hockey", "video games", "sleeping"),
  favourite_number = c(2, 7, 2, 7, 3, 3)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


I see a bar graph. The x-axis is labelled "github_username," and has six values with each individual's username. Each bar is the person's favorite color. The y-axis is labelled "favourite_number," and each bar reaches to the y-value of the person's favourite number.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Student Username", 
          y = "Selected Number",
          title = "Bar Graph Example")
```

I used ?labs and found that the labs() command is used for labels and labelling.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

It would probably not be a very good visualization because there would be very few repeats for any given hobby, making a very wide and short bar graph. It would make more sense to display the data using a list in order of each hobby's frequency with repeated numbers -- For example: '1' has 4 students in one hobby, '2' has 3 students in each of five hobbies, '7' has 2 students in each of eleven hobbies, and '18' has 1 student in each of twenty-three hobbies.
